ML model comparison

### 2020-10-04 src/s_ml_comparison.Rmd
more 8 schools analysis

fit_ncp <- sampling(
  model_ncp, data = eight_schools,
  iter = 2000, chains = 4, seed = 483892929, refresh = 0,
  control = list(adapt_delta = 0.95)
)

@@

tibble(var1=testing_data$V6, var2=testing_data$V10, chain=plda) %>% 
  ggplot(aes(x=var1, y=var2, colour=as.factor(chain))) +
  geom_jitter()
```

Cauchy model
```{r}
fit_nom <- stan(file = 'cauchy_nom.stan', seed = 7878,
                refresh = 0)
x <- rstan::extract(fit_nom, permuted=F)
temp1 <- f_replicate_ml_simple(x, "gbm", tunegrid_gbm)
temp <- f_replicate_ml_simple_gridded(x, "rf", tibble(mtry=1))
temp$a_accuracy

fit_alt1 <- stan(file = 'cauchy_alt_1.stan',
                 seed = 7878, refresh = 0)
x <- rstan::extract(fit_alt1, permuted=F)
temp1 <- f_replicate_ml_simple(x, "gbm", tunegrid_gbm)
temp <- f_replicate_ml_simple_gridded(x, "rf", tibble(mtry=1))
temp$a_accuracy
```

>>>>

fit_ncp <- sampling(
  model_ncp, data = eight_schools,
  iter = 40000, chains = 4, seed = 483892929, refresh = 0,
  control = list(adapt_delta = 0.95)
)

@@

tibble(var1=testing_data$V7, var2=testing_data$V15, chain=plda) %>% 
  ggplot(aes(x=var1, y=var2, colour=as.factor(chain))) +
  geom_jitter() +
  geom_smooth(method="lm", se=F)

tibble(var1=testing_data$V7, var2=testing_data$V15, chain=plda) %>% 
  ggplot(aes(x=var1, colour=as.factor(chain))) +
  stat_density(fill="none", position="identity")

hist(map_dbl(seq(1, 8, 1), function(i) cor(testing_data %>% filter(chain==i) %>% select(-chain) %>% as.matrix())[7, 15]))
```

Visualise between-chain correlation
```{r}
x <- split_data(x_ncp)
cors <- map(seq(1, dim(x)[2], 1), ~cor(x[, ., ]))
m_sd <- matrix(nrow = 19, ncol = 19)
for(i in 1:19)
  for(j in 1:19)
    m_sd[i, j] <- sd(map_dbl(seq(1, dim(x)[2], 1), ~cors[[.]][i, j]))
tmp <- which(m_sd == max(m_sd), arr.ind = TRUE)
a <- tmp[1,1]
b <- tmp[1,2]
m_sd[a, b]
colnames(r)[a] <- "a"
colnames(r)[b] <- "b"

r %>% 
  ggplot(aes(x=a, y=b, colour=as.factor(chain))) +
  geom_jitter(alpha=0.1) +
  geom_smooth(method="lm", se=F)

r %>% 
  select(chain, a, b) %>% 
  melt(id.vars="chain") %>% 
  ggplot(aes(x=value, colour=as.factor(chain), group=as.factor(chain))) +
  stat_density(fill="none", position = "identity") +
  facet_wrap(~variable)

r %>% 
  select(chain, a, b) %>% 
  melt(id.vars="chain") %>% 
  group_by(variable, chain) %>% 
  summarise(value=mean(value)) %>% 
  ggplot(aes(x=as.factor(chain), y=value)) +
  geom_point() +
  facet_wrap(~variable)

r %>% 
  select(chain, a, b) %>% 
  melt(id.vars="chain") %>% 
  group_by(variable, chain) %>% 
  summarise(value=quantile(value, 0.95)) %>% 
  ggplot(aes(x=as.factor(chain), y=value)) +
  geom_point() +
  facet_wrap(~variable)
```

How R* varies with hyperparameters
```{r}
x <- x_ncp

f_run_gbm <- function(x, n.trees_, int.depth_){
  return(f_replicate_ml_simple(x, "gbm", expand.grid(interaction.depth=c(int.depth_), 
                             n.trees = n.trees_,
                             shrinkage=c(0.1),
                             n.minobsinnode=10)))
}

hypers <- tibble(
       n.trees=c(50, 50, 100, 200, 200, 200, 200, 400, 400, 1000),
       int.depth=c(3,5,3,3,5,7,9,5,9,11))
k <- 1
niter <- 20
m_results <- matrix(nrow = nrow(hypers) * niter, ncol=4)
for(i in 1:nrow(hypers)){
  for(j in 1:niter){
    tree <- hypers$n.trees[i]
    depth <- hypers$int.depth[i]
    temp <- f_run_gbm(x, tree, depth)
    m_results[k, ] <- c(tree, depth, j, temp)
    k <- k + 1
  }
}
colnames(m_results) <- c("n.tree", "int.depth", "iter", "r_star")
m_results <- m_results %>% 
  as.data.frame()
saveRDS(m_results, "../data/8_schools_gbm_hyper.rds")
m_results %>% 
  group_by(n.tree, int.depth) %>% 
  summarise(lower=quantile(r_star, 0.25),
            middle=median(r_star),
            upper=quantile(r_star, 0.75)) %>% 
  ggplot(aes(x=as.factor(n.tree), y=middle, color=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position = position_dodge2(width=0.2)) +
  ylim(0.95, NA) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int.depth", palette = "Dark2") +
  xlab("# tree") +
  ylab("R*")
```

Try gbm function itself to optimise hyperparameters
```{r}
x <- x_ncp
x <- split_data(x)

rand_samples <- sample(1:nrow(r), 0.7 * nrow(r))
training_data <- r[rand_samples, ]
testing_data <- r[-rand_samples, ]

gbmFit <- train(chain ~ ., data = training_data, 
               method="gbm",
               tuneGrid = expand.grid(
       n.trees=c(50, 200, 2000),
       interaction.depth=c(3,11, 17),
       shrinkage=c(0.1),
             n.minobsinnode=c(10)))
plda <- predict(object=gbmFit, newdata=testing_data)
a_accuracy <- 
  tibble(predicted=plda, actual=testing_data$chain) %>%
  mutate(correct=if_else(predicted==actual, 1, 0)) %>% 
  summarise(mean(correct)) %>% 
  pull()
a_accuracy * n_distinct(training_data$chain)
varImp(gbmFit)
```

# Cauchy model
```{r}
# fit_nom <- stan(file = 'cauchy_nom.stan', seed = 7878,
#                 refresh = 0)
# x <- rstan::extract(fit_nom, permuted=F)
# temp1 <- f_replicate_ml_simple(x, "gbm", tunegrid_gbm)
# temp <- f_replicate_ml_simple_gridded(x, "rf", tibble(mtry=1))
# temp$a_accuracy

fit_alt1 <- stan(file = 'cauchy_alt_1.stan',
                 seed = 7878, refresh = 0)
x <- rstan::extract(fit_alt1, permuted=F)
# temp1 <- f_replicate_ml_simple(x, "gbm", tunegrid_gbm)
# temp <- f_replicate_ml_simple_gridded(x, "rf", tibble(mtry=1))
# temp$a_accuracy

hypers <- tibble(
       n.trees=c(50, 50, 100, 200, 200, 200, 200, 400, 400, 1000),
       int.depth=c(3,5,3,3,5,7,9,5,9,11))
k <- 1
niter <- 3
m_results <- matrix(nrow = nrow(hypers) * niter, ncol=4)
for(i in 1:nrow(hypers)){
  for(j in 1:niter){
    tree <- hypers$n.trees[i]
    depth <- hypers$int.depth[i]
    temp <- f_run_gbm(x, tree, depth)
    m_results[k, ] <- c(tree, depth, j, temp)
    k <- k + 1
  }
}
```
